SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-05 scipy-1.0/covlett.tex
Draft in 3 prospective reviewers for cover letter
Use more appropriate suggestion for 3rd reviewer; switch to enumerate

>>>>

\begin{enumerate}
    \item Alan Edelman, \texttt{edelman@math.mit.edu}, co-creator of Julia
    programming language and Faculty at MIT.
    \item William Stein, \texttt{wstein@gmail.com}, originator and
    lead developer of SageMath.
    \item Kazunori Akiyama, \texttt{kazu@haystack.mit.edu}, first author
    of event horizon imaging paper that cites SciPy.
\end{enumerate}
